Thermodynamic fragments in magic state theories

### 2020-11-28 appendix.tex
Added standard Lorenz curve expressions for all cases. Tidied up Strange state section and appendix

\section{Area monotone}
\label{app:areamono}

@@

\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:test1}%
    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:test2}%
    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }
    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
    }%
    \label{fig:test}
\end{figure}

>>>>

\section{Lorenz curve properties}
\label{app:lc_properties}

\subsection{Area monotone}\label{app:areamono}

\begin{figure}[t]%
    \centering
    \subfigure[][]{%
    \label{fig:test1}%
    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:test2}%
    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }
    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
    }%
    \label{fig:test}
\end{figure}

@@

\section{Technical derivations for standard Lorenz curves}
\label{app:lcsu_technical}

\subsection{Binomial distributions and error bounds}\label{app:phi}
Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
This scenario describes the construction of an $n$-copy Strange state Wigner distribution from a single-copy as presented in~\cref{sec:lcsu}.
The experiment is described by binomial statistics and we write down the sum over an even number of successful trials $\Phi_+$ (over an odd number of successful trials $\Phi_-$),
\begin{align}	
	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp_app} \\
	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
	&\text{for odd integers } \mmf\in[1,\nnf]. \label{eq:fn_app}
\end{align}
Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of standard Lorenz curves.

We define the classical entropy of a $p$-coin as well as the classical relative entropy between a $p$-coin and a $q$-coin,
\begin{align}
	S(p) &\coloneqq -p\log{p} -(1-p)\log{(1-p)}, \label{eq:ent}\\
	\ent{p}{q} &\coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}. \label{eq:ent_rel}
\end{align}
They are symmetric in the sense that $S(p) = S(1-p)$ and $\ent{p}{q} = \ent{1-p}{1-q}$.

A useful result is the entropic bound on a combination~\cite{cit:ash}.
\begin{lemma}\label{lem:comb_bounds}
	For all $\mmf\in [1,\nnf-1]$,
	\begin{align}
		&\left[ 8\mmf\left(1-\frac{\mmf}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\mmf}{\nnf}\right)} \leq \binom{\nnf}{\mmf} \leq \\
		&\left[ 2\pi \mmf\left(1-\frac{\mmf}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\mmf}{\nnf}\right)}.
	\end{align}
\end{lemma}
\begin{proof}
	For $\mmf = 1,2, \nnf-1, \nnf-2$ check by direct calculation.	
	For all other cases, use Stirling's approximation. 
	\nick{CITE}
\end{proof}
With the help of this lemma, we directly arrive at 
\begin{theorem}\label{thm:bounds_strict}
	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(\mmf; \nnf, p) \geq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 16\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
		&\text{2. } \Phi_+(\mmf; \nnf, p) \leq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 4\pi\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
		&\text{3. } \Phi_-(\mmf; \nnf, p) \geq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 16(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd }\mmf\in [1,\nnf] \\
		&\text{4. } \Phi_-(\mmf; \nnf, p) \leq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 4\pi(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd } \mmf\in [1,\nnf]
		\end{split}
	\end{align*}
\end{theorem}
\begin{proof}
	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
\end{proof}

\iffalse % LOOSE BOUNDS & PLOT - START
The experiment is described by binomial statistics and we define the left tail of the cumulative binomial distribution,
\begin{equation}\label{eq:phil}
	\Phi_\ell(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j},
\end{equation}
where $m\in [0,n]$.

The symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution dictates that
\begin{align}\label{eq:phi_reverse}
	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1],
\end{align}
Entropic bounds on $\Phi_\ell$~\cite{cit:ash}.
\begin{lemma}\label{lem:phil_bounds}
	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
		&\hspace{14pt} m\in [0,n-2]
		\end{split}
		\\
		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
	\end{align*}
\end{lemma}
\begin{proof}
	\nick{cite proof}
\end{proof}
Loose bounds follow
\begin{lemma}\label{lem:bounds_loose}
	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_{\pm}(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
		&\text{2. } \Phi_{\pm}(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
		&\text{3. } \Phi_{\pm}(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
		&\hspace{14pt} m\in [0,n-2]
		\end{split}
	\end{align*}
\end{lemma}
\begin{proof}
	\nick{paste proof}
\end{proof}

We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
\begin{figure}[b]
    \centering
    \includegraphics[scale=0.4]{figs/lc_bounds.pdf}
    \caption{\textbf{Lorenz curves and bounding curves.} 
    The figure explores the distillation process of a 10-copy $0.25$-noisy Strange state to a 4-copy $0.05$-noisy Strange state in the unital fragment.
    Clearly, by looking at the Lorenz curves, the distillation process is possible.
    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
    }
    \label{fig:lc_bounds}
\end{figure}
\fi % LOOSE BOUNDS & PLOT - END

\subsection{Standard Lorenz curve elbow coordinates}\label{app:lcsu_coord_elb}
The Wigner distribution of the $\NN$-copy qutrit maximally mixed state $\left(\id/3\right)\too{\NN}$ is the uniform distribution 
\begin{equation}\label{eq:wu}
	\W{\left(\id/3\right)\too{\NN}} = \Bigg( \overbrace{\frac{1}{9^\NN}, \dots, \frac{1}{9^\NN}}^{9^\NN} \Bigg).
\end{equation}
The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\noisys(\epsilon)$ in the unital fragment is a permutation of 
\begin{equation}\label{eq:wsu}
	\W{\noisys(\epsilon)} = \Bigg( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \Bigg)
\end{equation}
The two distinct components are plotted~\cref{fig:noisys} as a function of noise. 
It is clear that in the unital fragment the Strange state contains Wigner negativities in the regime $0 \leq \epsilon \leq \tfrac{3}{4}$.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.7]{figs/noisys.pdf}
    \caption{\textbf{Wigner components of the noisy Strange state.} 
    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
    }
    \label{fig:noisys}
\end{figure}

The Wigner distribution of the $\NN$-copy $\epsilon$-noisy Strange state $\noisysN$ in the unital fragment is given by the convolution $\W{\noisysN} = \rm{W}_{\noisys(\epsilon)}\too{\NN}$.
In general, $\noisysN$ contains $\NN + 1$ distinct components, labelled $0,\dots, \NN$.
We present the distinct Wigner components of $\noisysN$ along with their multiplicites in~\cref{tab:lcsu}.
Note that LHS (RHS) refers to elbow coordinates $\ii$ on the left of and including (right of) the maximum, precisely
\begin{align}
&\text{LHS: } 0 \leq \ii \leq \frac{\lfloor \NN \rfloor}{2}; \\
&\text{RHS: } \frac{\lfloor \NN \rfloor}{2}+1 \leq \ii \leq \NN.
\end{align}
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$\mlt_{\ii}(\NN, \epsilon)$} & \multicolumn{1}{|c}{$w_{\ii}(\NN, \epsilon)$} \\[0.5ex]\hline
    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\
    & & RHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $8^{2\ii+1}\binom{\NN}{2\ii+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii+1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii-1}$ \\
    & & RHS & $8^{\NN-2\ii-1}\binom{\NN}{2\ii+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii+1}$ \\ \hline
    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\
    & & RHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\
    & & RHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\ \hline
  \end{tabular}
  \caption{Wigner components $w_{\ii}(\NN, \epsilon)$ of $\noisysN$ along with their multiplicities $\mlt_{\ii}(\NN, \epsilon)$ in decreasing order in $\ii,\ 0 \leq \ii \leq \NN$.
  The order changes depending on the noise level $\epsilon$, the parity of the number of copies $\NN$ and the parity of the components (LHS vs RHS).
  Multiplication $2\ii$ is considered modulo $(\NN+1)$.}
  \label{tab:lcsu}
\end{table}

For example, the distribution of state $\noisys(0)\too{2}$ is
\begin{equation*}
	\begin{split}
	\rm{W}_{\noisys(0)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \\
	&\overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \Bigg)
	\end{split}
\end{equation*}

Every standard Lorenz curve contains $\NN$ elbows, labelled by 
\begin{equation*}
\{(x_{\ii}, L_{\ii})\}_{\ii=-1,0,\dots,\NN}\ ,
\end{equation*}
where the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$ are also included.
The maximum is the $(\lfloor \NN \rfloor/2)$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
\begin{align}
	x_{\lfloor \NN \rfloor/2} &= \frac{1}{2}\left(1 + \left(\frac{7}{9}\right)^\NN\right), \\
	L_{\lfloor \NN \rfloor/2} &= \frac{1}{2}\left (1 + \left(\frac{15 - 8\epsilon}{9}\right)^\NN \right).
\end{align}
%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]

Expressions for all the elbow coordinates follow from summing up the Wigner components in decreasing order and we present the elbow coordinates for standard Lorenz curves in~\cref{tab:lcsu_coord_elb_app}.
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{\ii}$} & \multicolumn{1}{|c}{$L_{\ii}$} \\[0.5ex]\hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\NN/2} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
  \end{tabular}
  \caption{Standard Lorenz curves elbow coordinates.
  The expresion depends on the noise level $\epsilon$, the parity of the number of copies $\NN$ and the location of the elbow relative to the maximum (LHS vs RHS).
  Multiplication $2\ii$ is considered modulo $(\NN+1)$.
  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$.
  }
  \label{tab:lcsu_coord_elb_app}
\end{table}

\subsection{Standard Lorenz curve coordinates}\label{app:lcsu_coord}
We can get explicit expressions for all $9^{\NN}$ points of the standard Lorenz curve $\lc{\noisysN}{\id/3}$, in terms of the elbow coordinates:
\begin{align}
    x_{\ii\jj} &= \left( 1-\frac{\jj}{\mlt_{\ii}} \right) x_{\ii-1} + \frac{\jj}{\mlt_{\ii}} x_{\ii}, \label{eq:x}\\
    L_{\ii\jj} &= \left( 1-\frac{\jj}{\mlt_{\ii}} \right) L_{\ii-1} + \frac{\jj}{\mlt_{\ii}} L_{\ii} \label{eq:l}
\end{align}
for $\jj = 1,\dots,\mlt_{\ii}$ and $\ii=0,\dots,\NN$, where multiplicities $\mlt_\ii = \mlt_\ii(\NN, \epsilon)$ are given in~\cref{tab:lcsu}.

For visualisation purposes, we plot the Lorenz curve of state $\noisys(0)\too{2}$.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.6]{figs/lcpoints.pdf}
    \caption{\textbf{All points on the Lorenz curve are uniformly distributed.}
    \cref{eq:x,eq:l}) capture the coordinates of all points up to the maximum.
    }
    \label{fig:lc}
\end{figure}

Consider the state 
\begin{equation*}
    \noisys(\epsilon)\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm},
\end{equation*} %\noisys(\tt, \epsilon, \mm) \coloneqq 
with $\tt + \mm = \NN$.

Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
The new point coordinates are given by:
\begin{align}
    &x_{\ii\jj\kk} = \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
    &L_{\ii\jj\kk} = \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}\\
    &\text{where } p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\mm}}{9^{\mm} \mlt_{\ii}} \nonumber\\
    &\text{for } \ii=0,\dots,\tt,\ \jj = 1,\dots,\mlt_{\ii}(\tt, \epsilon') \text{ and } \kk = 1,\dots,9^{\mm}. \nonumber
\end{align}

We can unify the indices, by introducing a single index
\begin{equation}
    \II(\ii,\jj,\kk) \coloneqq \kk + \left[ (\jj-1) + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\mm},
\end{equation}
so that $\II=1,2,\dots, 9^{\NN}$.
The elbow coordinates correspond to 
\begin{equation}
	\II(\ii, \mlt_{\ii}(\tt, \epsilon'), 9^{\mm}) = \sum_{\dummy=0}^{\ii} \mlt_{\dummy}(\tt, \epsilon'),\ \ii= 0,\dots,\tt.
\end{equation}
The index function $\II$ is bijective, i.e.
\begin{equation}
	(\ii,\jj,\kk) = (\ii',\jj',\kk') \Leftrightarrow \II(\ii,\jj,\kk) = \II(\ii',\jj',\kk').
\end{equation}

\subsection{Strange state MSD in the unital fragment}\label{app:lc_compare}
Consider the Strange state MSD process in the unital fragment,
\begin{equation}\label{eq:su_conversion}
    \noisysn \xrightarrow{\mathcal{O}_{\id/3}} \noisys(\tt, \epsilon', \mm),\ \nn = \tt + \mm.
\end{equation}
We denote initial state indices without a prime and target state indices with a prime,
\begin{align}
    \II(\ii,\jj,\kk=1) &= \jj + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\nn, \epsilon), \\
    \II'(\ii',\jj',\kk') &= \kk' + \left[ (\jj'-1) + \sum_{\dummy=0}^{\ii'-1} \mlt_{\dummy}(\tt, \epsilon') \right]9^{\mm}.
\end{align}

Pointwise Lorenz curve comparison requires $x_{\II} = x_{\II'}$, so the question is: 
\begin{center}
\emph{Given a triplet $(\ii',\jj',\kk')$, what is the tuple $(\ii,\jj)$ such that $\II(\ii,\jj) = \II'(\ii',\jj',\kk')$?}
\end{center}

As a basic example, consider the process 
\begin{equation}
\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
\end{equation}
We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
\begin{equation}
	L_{\II(\ii,\jj)} \geq L'_{\II'(0, 1, 81)}
\end{equation}
where the first multiplicity of the target state is $m_0 = 1$.
The multiplicities of the initial state are $(1, 384, 4096)$.

The challenge is to find $\ii,\jj$ such that $i(\ii,\jj) = i'(0,1,81)$.
\nick{By trial and error}, we find that $(\ii,\jj) = (1, 80)$.
Now we can use~\cref{eq:lcsu_lcoord} to directly calculate
\begin{align*}
	L'_{i'(0,1,81)} &= L'_0 = \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^2 \Phi_+\left(0;2,4\frac{3-\epsilon}{15-8\epsilon}\right), \\
	L_{i(1, 80)} &= \left(1-\frac{80}{384} \right) L_0 + \frac{80}{384} L_1 \\
	\begin{split}
	&= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^4 \bigg[ \frac{19}{24} \Phi_+\left(0;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \\ 
	&\qquad + \frac{5}{24}\Phi_+\left(2;4,4\frac{3-\epsilon}{15-8\epsilon}\right) \bigg],
	\end{split}
\end{align*}
and then compare them.

\subsection{Lorenz curve independent constraints}\label{app:lc_constraints}

\begin{theorem}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.

	Let $\tt$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\tt\}$ be their locations.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,\tt$.
\end{theorem}
\begin{proof}	
	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii = 1,\dots,\tt$.

	Conversely, assume that $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii = 1,\dots,r$.
	First, let $x_0 = 0$ and $x_{\tt+1} = 1$, so that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{\tt+1}) = \lc{\tau}{\sigma}(x_{\tt+1}) = 1$.
	Hence, we can extend the set of elbows $E$ to $E' = E \cup \{x_0, x_{\tt+1}\}$.

	Pick two consecutive locations $x_{\ii}, x_{\ii+1}$ in $E'$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_{\ii}, \lc{\tau}{\sigma}(x_{\ii}))$ and $(x_{\ii+1}, \lc{\tau}{\sigma}(x_{\ii+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_{\ii}, \lc{\rho}{\sigma}(x_{\ii}))$ and $(x_{\ii+1}, \lc{\rho}{\sigma}(x_{\ii+1}))$.
	This is illustrated in~\cref{fig:elbows_proof}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
    }
    \label{fig:elbows_proof}
\end{figure}

	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_{\ii}, x_{\ii+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
	This argument can be made in all intervals $[x_{\ii}, x_{\ii+1}]$ with $\ii=0,\dots,\tt$, so the proof is complete.
\end{proof}
This theorem is of practical importance in calculating the necessary distillation constraints derived via majorization.
